The KMOS Deep Survey (KDS): dynamical measurements of $z\sim3.5$ main sequence galaxies\thanks{Based on observations obtained at the Very Large Telescope of the European Southern Observatory. Programme IDs: }

### 2017-03-22 paper.tex
Just getting started on Ross changes

% The list of authors, and the short list which is used in the headers.
% If you need two or more lines of authors, add an extra line using \newauthor
%\author[O.J. Turner et al.]{
%O. J. Turner,$^{1,2,\thanks{E-mail: turner@roe.ac.uk (OJT)}}$
%M. Cirasuolo,$^{1,2}$
%C. M. Harrison,$^{2,3}$
%J. Dunlop,$^{1}$
%R. J. McLure,$^{1}$\newauthor
%A. M. Swinbank$^{3,4}$
%H. L. Johnson$^{3,4}$
%D. Sobral$^{5}$
%J. Matthee$^{6}$
%R. M. Sharples$^{3,4}$
%\\
%$^{1}$SUPA\thanks{Scottish Universities Physics Alliance}, Institute for Astronomy, University of Edinburgh, Royal Obervatory, Edinburgh EH9 3HJ\\
%$^{2}$European Southern Observatory, Karl-Schwarzschild-Str. 2, 85748 Garching b. M{\"u}nchen, Germany\\
%$^{3}$Centre for Extragalactic Astronomy, Durham University, South Road, Durham, DH1 3LE, U.K.\\
%$^{4}$Institute for Computational Cosmology, Durham University, South Road, Durham, DH1 3LE, U.K.\\
%$^{5}$Department of Physics, Lancaster University, Lancaster, LA1 4BY, U.K.\\
%$^{6}$Leiden Observatory, Leiden University, PO Box 9513, NL-2300 RA Leiden, the Netherlands}

\author[O.J. Turner et al.]{
O. J. Turner,$^{1,2,\thanks{E-mail: turner@roe.ac.uk}}$
\\
$^{1}$SUPA\thanks{Scottish Universities Physics Alliance}, Institute for Astronomy, University of Edinburgh, Royal Obervatory, Edinburgh EH9 3HJ\\
$^{2}$European Southern Observatory, Karl-Schwarzschild-Str. 2, 85748 Garching b. M{\"u}nchen, Germany
}

@@

% Abstract of the paper
\begin{abstract}
We present dynamical measurements for 77 star-forming galaxies at $z\sim3.5$ in the mass range $9.5 < log(M_{\star}[M_{\odot}]) < 10.5$ from the KMOS (K-band Multi-Object Spectrograph) Deep Survey (KDS).
These measurements constrain the internal dynamics, the intrinsic velocity dispersions $\sigma_{int}$ and rotation velocities, $V_{C}$, of galaxies in the high-redshift Universe.
We have made careful comparisons to other samples which have been selected consistently, span a wide redshift baseline and use ionised gas emission to trace galaxy dynamics. 
The mean dispersion value of the galaxies in our sample is $\sigma_{int} = 70.8^{+3.3}_{-3.1} kms^{-1}$, consistent with the increase of $\sigma_{int}$ with redshift reported up to $z\sim3$ in other samples.
However only $34 \pm 8\%$ of our galaxies are rotationally-dominated ($V_{C}/\sigma_{int}$ > 1), with the sample average $V_{C}/\sigma_{int}$ value much less than at lower redshift.
The rotation dominated KDS galaxies show no clear offset from the local rotation velocity-stellar mass (i.e. $V_{C}-M_{\star}$) relation, although a smaller fraction of the galaxies are on the relation due to the increase in the dispersion dominated fraction.
These observations are consistent with a simple equilibrium model picture, in which random motions are boosted in high-redshift galaxies by the increase in gas fractions, accretion efficiency, specific star-formation rate and stellar feedback.
These random motions are likely to provide significant pressure support against gravity on the galactic disk scale.
\end{abstract}

@@

The galaxy population at all redshifts appears to be bimodal in many physical properties \citep[e.g. as described in][]{Dekel2006}, with a preference for the most massive galaxies to lie in the red sequence, characterised by red optical colours, low Star Formation Rates (SFRs) and spherical morphologies, and less massive galaxies in the blue sequence, characterised by blue colours, high star formation rates and disky morphologies. 
For these blue, star-forming galaxies (SFGs) there is a roughly linear correlation between SFR and stellar mass ($M_{\star}$) \citep[e.g.][]{Daddi2007,Noeske2007,Elbaz2007}, in the sense that galaxies which have already accumulated a larger stellar population tend to have higher SFRs.
This correlation, or `main sequence' underpins the `equilibrium model', in which the SFR of galaxies is regulated by the availability of gas, with outflows and accretion events sustaining the galaxy gas reservoirs in a rough equilibrium as the galaxy evolves \citep[e.g.][]{Dave2012,Lilly2013,Saintonge2013}.
The main sequence has been studied comprehensively, using multi-wavelength SFR tracers, between $0 < z < 3$ \citep[e.g.][]{Rodighiero2011,Karim2011,Whitaker2012,Behroozi2013b,Whitaker2014,Rodighiero2014,Speagle2014,Pannella2014,Sobral2014,Sparre2015,Lee2015,Schreiber2015,Renzini2015,Nelson2016}, showing evolution of the relation towards higher SFRs at fixed $M_{\star}$ with increasing redshift, reflecting the increase of the cosmic Star Formation Rate Density (SFRD) in this redshift range \citep{Madau_2014}.
At each redshift slice it has been suggested that galaxies on the main sequence evolve secularly as regulated by their gas reservoirs, and so selecting such populations offers the chance to explore the evolution of the physical properties of typical SFGs across cosmic time.
This assumes that high-redshift main sequence galaxies are the progenitors of their lower redshift counterparts, which may not be the case \citep[e.g.][]{Gladders2013,Kelson2014,Abramson2016b} and also assumes that we can learn about galaxy evolution (i.e. how individual galaxies develop in physical properties over time) by studying the mean properties of populations at different epochs.

The picture is complicated by the addition of major and minor galaxy mergers which can rapidly change the physical properties of galaxies \citep[e.g.][]{Toomre1977,Lotz2008,Conselice2011,Conselice2014} and the relative importance of in-situ, secular stellar mass growth vs. stellar mass aggregation via mergers is the subject of much work involving both observations and simulations \citep[e.g.][]{Robaina2009,Kaviraj2012,Stott2013,Lofthouse2016,Qu2016}. 
To account for the growing number density of quiescent galaxies from z$\sim 2.5$ to the present day \citep[e.g.][]{Bell2004,Faber2007,Brown2007,Ilbert2010,Brammer2011,Muzzin2013,Buitrago2013} there must also be processes which shut off star-formation within main sequence galaxies (i.e. quenching) which, to explain observations, is a function of both mass and environment \citep{Peng2010,Darvish2016}.

@@

This paper focusses on the third question by deriving and interpreting the spatially resolved kinematics of the KDS galaxies, particularly the rotation velocities and velocity dispersions, using the [O~{\sc III}]$\lambda$5007 emission line, discussing what we can learn about the nature of galaxy formation at $z \sim 3.5$ and forming evolutionary links with lower redshift work.
We seek also to minimise the impact of systematic differences introduced by the differing approaches in defining and extracting kinematic parameters when interpreting these trends.  
By making use of KMOS we have been able to study [O~{\sc III}]$\lambda$5007 emission in 77 galaxies with integration times ranging between 7.5-9 hours on source, with these galaxies, which span the mass range $9.5 < log(M_{\star}[M_{\odot}]) < 10.5$, roughly tripling the number of galaxies observed in IFS at $z > 3$. \\

@@

\begin{figure*}
\centering
\includegraphics[width=0.8\textwidth]{main_sequence_hor.png}
\caption{We plot the location of 48 KDS galaxies (see \cref{subsubsec:sample_summary}) in the SFR versus M$_{\star}$ plane, with filled symbols showing galaxies detected in [O~{\sc III}]$\lambda$5007 and open symbols showing those which were not detected. 
Also plotted with the small grey points are individual SFGs from the 3D-{\em HST} survey  \protect\citep{Brammer2012,Momcheva2016} at 2 $<$ z $<$ 3 as a reference for the typical relationship between SFR and $M_{\star}$.
The solid black lines and the dashed line show the $z\sim2.5$ broken power-law and quadratic fit to the main sequence respectively, described in \protect\cite{Whitaker2014}.
We include the MS relation described in \protect\cite{Speagle2014} and given in equation \protect\ref{eq:speagle_ms} throughout the text as the green line. 
Within the typical uncertainties (see error bars) the KDS sample is representative of $z\sim3$ SFGs.}
\label{fig:main_sequence}
\end{figure*}

Our data for the 77 KDS targets were observed using KMOS.
KMOS is a second generation IFS mounted at Nasmyth focal plane on UT1 at the VLT.
The instrument has 24 moveable pickoff arms, each with an integrated IFU, which patrol a region 7.2$^{\prime}$ in diameter on the sky, providing considerable flexibility when selecting sources for a single pointing.
The light from each set of 8 IFUs is dispersed by a single spectrograph and recorded on a 2k$\times$2k Hawaii-2RG HgCdTe near-IR detector, so that the instrument is comprised of three effectively independent modules.
Each IFU has 14$\times$14 spatial pixels which are 0.2$^{\prime\prime}$ in size, and the central wavelength of the K-band grating has spectral resolution of $R \sim 4200$ (H-band $R \sim 4000$).
\subsubsection{Observations}\label{subsubsec:Obs}
To achieve the science goals of the KDS the target galaxies at $3 < z < 3.8$ were observed in both the K-band, into which the [O~{\sc III}]$\lambda$5007 and $H\beta$ lines are redshifted, and the H-band, into which the [O~{\sc II}]$\lambda$3727,$\lambda$3729 doublet is redshifted, to facilitate both dynamical and chemical abundance measurements.
The GOODS-S pointings were observed in the H and K-bands separately, however due to loss of observing time the SSA22 galaxies were observed with the KMOS HK filter, which has the disadvantage of effectively halving the spectral resolution, but allows for coverage of the H-band and K-band regions simultaneously. \\

@@

\subsubsection{SED fitting and main sequence}\label{subsubsec:sed_fitting}
We use SED modelling to constrain simultaneously the $M_{\star}$ and SFR of the KDS targets.
During the SED modelling we assume solar metallicity stellar templates and make use of \cite{Calzetti2000} reddening law with exponentially declining SFRs in both GOODS-S and SSA22.
A Chabrier IMF is used with a reduced set of BC03 \citep{Bruzual2003} templates in the fitting procedure.
We have also computed the quantities using 0.2Z$\odot$ templates, finding stellar masses for the galaxies which are on average 0.1 dex lower, but this change does not affect the conclusions of this work.
The median stellar mass for the full observed samples in both GOODS-S and SSA22 is $log(M_{\star}[M_{\odot}]) = 10.0$.
In SSA22 29 targets (36\% of the full KDS sample) do not have SFR measurements due to having J and K-band detections lower than 2-$\sigma$ significance.
For these objects we are able to estimate robust stellar masses from the available photometry, noting that the median of stellar mass distribution is $\sim 0.3$ dex lower than the median stellar mass in GOODS-S.
In Figure \ref{fig:main_sequence} we plot the M$_{\star}$ and SFR `main sequence' for the 64\% of KDS galaxies with SFR measurements, in combination with the derived physical properties of $\sim 10,000$ SFGs at $2.5 < z < 3.5$  (based upon the `z\_best classification flag') from the 3D-{\em HST} survey \citep{Brammer2012,Momcheva2016}.
We also plot both the linear-break and quadratic $z\sim 2.5$ main sequence fits to the 3D-{\em HST} data described in \cite{Whitaker2014} with the solid and dashed black lines as well as the main sequence relation described in \cite{Speagle2014} given in equation \ref{eq:speagle_ms}, evaluated at $z\sim3.5$ where the age of the universe is 1.823 Gyr, with the green line.

@@

The difference in position of these relations highlights the main sequence evolution towards higher SFRs at fixed $M_{\star}$ between $z\sim2.5-3.5$.
The KDS galaxies scatter, within the errors, consistently above and below the z$\sim3$ main sequence, indicating that they represent typical SFGs at this redshift.

@@

ID              & RA       & Dec       & z     & K$_{AB}$     & $log(M_{\star}[M_{\odot}])^{a}$ & SFR$_{SED}$[$M_{\odot}yr^{-1}]$$^{b}$ & $b/a$ & i$^{\circ}$$^{c}$ & PA$_{morph}^{\circ}$ & R$_{1/2}$(kpc)$^{d}$ \\

@@

We plot the relationship between $V_{C}$ and $M_{\star}$ for the isolated field sample in the left panel of Figure \ref{fig:tf_relation}.
In \cite{Harrison2017}, the inverse stellar mass Tully-Fisher relation relation is fit to $\sim400$ $9.5 < log(M_{\star}[M_{\odot}]) < 10.5$ star-forming galaxies at $z\sim0.9$, measured to be rotationally dominated with $V_{C}/\sigma_{int} > 1$.
The data are used to constrain parameters `a' and `b' in the equation $logV_{C}=b+a[logM_{\star} - 10.0]$ (see their section 4.2) finding $a = 0.33 \pm 0.11$ and $b = 2.12 \pm 0.04$.
We plot this best fit relation with the solid green line, with the green shaded region giving the typical scatter of 0.2 dex along the velocity axis.
These $z\sim0.9$ parameters are consistent with the coefficients measured in the local universe, $a_{z=0} = 0.278 \pm 0.010$ and $b_{z=0} = 2.142 \pm 0.004$ , for a sample of $z<0.1$ disks from \cite{Reyes2011}, which are in a similar mass range to KROSS and traced with H$\alpha$ emission.
In \citep{Reyes2011} $V_{C}$ has been extracted at the same radius and we plot this $z\sim 0.1$ local relation as the dashed black line in the left panel of Figure \ref{fig:tf_relation}.
The agreement between these parameters derived at $z\sim0$ and $z\sim0.9$ suggests that there is no evolution of the slope/normalisation of the stellar mass Tully-Fisher relation for rotationally dominated star-forming galaxies between these limits. \\

@@

In a rotationally supported system, the circular velocity is set by the requirement to support the total mass in the system, i.e. the combination of gas mass, stellar mass and dark matter mass, against gravitational collapse.
$V_{C}$ increases with increasing total mass and so we would expect the systems with larger average stellar mass, assuming that these are indicative of systems with greater total mass, to have larger $V_{C}$, which appears generally to be the case in the right panel of Figure \ref{fig:tf_relation} where the KMOS$^{3D}$, GHASP and SINS galaxies have the largest inferred $V_{C}$ values.
Using the average $M_{\star}$ values and velocity extraction radii in the isolated field sample, $log(M_{\star}[M_{\odot}])=10.0$ and $2R_{1/2} = 3.2kpc$ respectively, and assuming simple, circular Keplerian orbits where the rotational motions alone support the mass of the system, we can calculate a rough lower limit of $\left<V_{C}\right>$ $>$ $125kms^{-1}$ for the baryonic material in the galaxies (since the inclusion of gas mass and dark matter mass would raise this estimate).
Indeed this value is similar to the mean $V_{C}$ value found in the KROSS sample for $log(M_{\star}[M_{\odot}])=10.0$ galaxies at $z\sim1$. \\

@@

We proceed to consider the cause of the high number of dispersion dominated galaxies in our sample and the obvious candidate is the increase of velocity dispersion with redshift \citep[e.g.][]{Genzel2006,Genzel2008,ForsterSchreiber2009,Law2009,Gnerucci2011,Epinat2012,Wisnioski2015}.
There are also some galaxies in our sample where the observed velocity field has obvious rotational structure and clearly reaches flattening (e.g. see \cref{fig:dispersion_dominated_galaxies} lbg\_24 with $log(M_{\star}[M_{\odot}])=9.75$), with inferred $V_{C}$ smaller than $\sigma_{int}$.
This suggests again that the increase in random motions could influence the rotational velocities and that the accumulation of a massive stellar population is necessary to stabilise a galaxy \citep[e.g.][]{Law2009,Law2012b,Law2012c,Newman2013,Wisnioski2015}.
These ideas are explored in the following sections.

@@

The mean KDS datapoint is in agreement with the scaling relation, plotted with the grey lines for $V_{C} = 125kms^{-1}$ and $log(M_{\star}[M_{\odot}])=10.0,10.3,10.6$ (note we have not shifted the datapoints to conform with a single $M_{\star}$ value as per \cite{Wisnioski2015}).
The lower $M_{\star}$ tracks suggest a flatter evolution of $\sigma_{int}$ with redshift, and indeed the surveys with lower average $M_{\star}$ (MASSIV, DYNAMO, LAW 2009, KROSS, AMAZE) have higher $\sigma_{int}$ than the surveys with larger average $M_{\star}$ (GHASP, KMOS$^{3D}$, SINS), although the exact values are sensitive to the choice of $Q_{crit}$ (shown to be $\sim1$ for the gas-rich disks observed at high-z e.g. \citealt{ForsterSchreiber2006,Genzel2011,Newman2013}) and $V_{C}$ in the equation shown in the top right of the left panel of Figure \ref{fig:sigma_and_v_sigma_w_redshift} (see \cref{sec:discussion}).
The tracks plotted in Figure \ref{fig:sigma_and_v_sigma_w_redshift} suggest the shape of the $\sigma_{int}$ evolution in galaxies of a particular stellar mass in the context of the equilibrium model, with these new results from the KDS providing strong observational constraints on the internal dynamics of main sequence galaxies between $z=3-3.7$.

>>>>

% The list of authors, and the short list which is used in the headers.
% If you need two or more lines of authors, add an extra line using \newauthor
%\author[O.J. Turner et al.]{
%O. J. Turner,$^{1,2,\thanks{E-mail: turner@roe.ac.uk (OJT)}}$
%M. Cirasuolo,$^{1,2}$
%C. M. Harrison,$^{2,3}$
%J. Dunlop,$^{1}$
%R. J. McLure,$^{1}$\newauthor
%A. M. Swinbank,$^{3,4}$
%H. L. Johnson,$^{3,4}$
%D. Sobral,$^{5}$
%J. Matthee,$^{6}$
%R. M. Sharples$^{3,4}$
%\\
%$^{1}$SUPA\thanks{Scottish Universities Physics Alliance}, Institute for Astronomy, University of Edinburgh, Royal Observatory, Edinburgh EH9 3HJ\\
%$^{2}$European Southern Observatory, Karl-Schwarzschild-Str. 2, 85748 Garching b. M{\"u}nchen, Germany\\
%$^{3}$Centre for Extragalactic Astronomy, Durham University, South Road, Durham, DH1 3LE, U.K.\\
%$^{4}$Institute for Computational Cosmology, Durham University, South Road, Durham, DH1 3LE, U.K.\\
%$^{5}$Department of Physics, Lancaster University, Lancaster, LA1 4BY, U.K.\\
%$^{6}$Leiden Observatory, Leiden University, PO Box 9513, NL-2300 RA Leiden, the Netherlands}

\author[O.J. Turner et al.]{
O. J. Turner,$^{1,2,\thanks{E-mail: turner@roe.ac.uk}}$
\\
$^{1}$SUPA\thanks{Scottish Universities Physics Alliance}, Institute for Astronomy, University of Edinburgh, Royal Observatory, Edinburgh EH9 3HJ\\
$^{2}$European Southern Observatory, Karl-Schwarzschild-Str. 2, 85748 Garching b. M{\"u}nchen, Germany
}

@@

% Abstract of the paper
\begin{abstract}
We present dynamical measurements for 77 star-forming galaxies at $z\sim3.5$ in the mass range $9.5 < log(M_{\star}/M_{\odot}) < 10.5$ from the KMOS (K-band Multi-Object Spectrograph) Deep Survey (KDS).
These measurements constrain the internal dynamics, the intrinsic velocity dispersions ($\sigma_{int}$) and rotation velocities ($V_{C}$) of galaxies in the high-redshift Universe.
We have made careful comparisons to other samples which have been selected consistently, span a wide redshift baseline and use ionised gas emission to trace galaxy dynamics. 
The mean dispersion value of the galaxies in our sample is $\sigma_{int} = 70.8^{+3.3}_{-3.1} kms^{-1}$, consistent with the increase of $\sigma_{int}$ with redshift reported up to $z\sim3$ in other samples.
However only $34 \pm 8\%$ of our galaxies are rotationally-dominated ($V_{C}/\sigma_{int}$ > 1), with the sample average $V_{C}/\sigma_{int}$ value much less than at lower redshift.
The rotation dominated KDS galaxies show no clear offset from the local rotation velocity-stellar mass (i.e. $V_{C}-M_{\star}$) relation, although a smaller fraction of the galaxies are on the relation due to the increase in the dispersion dominated fraction.
These observations are consistent with a simple equilibrium model picture, in which random motions are boosted in high-redshift galaxies by the increase in gas fractions, accretion efficiency, specific star-formation rate and stellar feedback.
These random motions are likely to provide significant pressure support against gravity on the galactic disk scale.
\end{abstract}

@@

The galaxy population at all redshifts appears to be bimodal in many physical properties \citep[e.g. as described in][]{Dekel2006}, with a preference for the most massive galaxies to lie in the red sequence, characterised by red optical colours, low Star Formation Rates (SFRs) and spherical morphologies, and less massive galaxies in the blue sequence, characterised by blue colours, high star formation rates and disky morphologies. 
For these blue, star-forming galaxies (SFGs) there is a roughly linear correlation between SFR and stellar mass ($M_{\star}$) \citep[e.g.][]{Daddi2007,Noeske2007,Elbaz2007}, in the sense that galaxies which have already accumulated a larger stellar population tend to have higher SFRs.
This correlation, or `main sequence' underpins the `equilibrium model', in which the SFR of galaxies is regulated by the availability of gas, with outflows and accretion events sustaining the galaxy gas reservoirs in a rough equilibrium as the galaxy evolves \citep[e.g.][]{Dave2012,Lilly2013,Saintonge2013}.
The main sequence has been studied comprehensively, using multi-wavelength SFR tracers, between $0 < z < 3$ \citep[e.g.][]{Rodighiero2011,Karim2011,Whitaker2012,Behroozi2013b,Whitaker2014,Rodighiero2014,Speagle2014,Pannella2014,Sobral2014,Sparre2015,Lee2015,Schreiber2015,Renzini2015,Nelson2016}, showing evolution of the relation towards higher SFRs at fixed $M_{\star}$ with increasing redshift, reflecting the increase of the cosmic Star Formation Rate Density (SFRD) in this redshift range \citep{Madau_2014}.
At each redshift slice it has been suggested that galaxies on the main sequence evolve secularly, as regulated by their gas reservoirs, meaning that selecting such populations offers the chance to explore the evolution of the physical properties of typical SFGs across cosmic time.
This assumes that high-redshift main sequence galaxies are the progenitors of their lower redshift counterparts, which may not be the case \citep[e.g.][]{Gladders2013,Kelson2014,Abramson2016b} and also assumes that we can learn about galaxy evolution (i.e. how individual galaxies develop in physical properties over time) by studying the mean properties of populations at different epochs.

The picture is complicated by the addition of major and minor galaxy mergers which can rapidly change the physical properties of galaxies \citep[e.g.][]{Toomre1977,Lotz2008,Conselice2011,Conselice2014} and the relative importance of in-situ, secular stellar mass growth vs. stellar mass aggregation via mergers is the subject of much work involving both observations and simulations \citep[e.g.][]{Robaina2009,Kaviraj2012,Stott2013,Lofthouse2016,Qu2016}. 
To account for the growing number density of quiescent galaxies from z$\sim 2.5$ to the present day \citep[e.g.][]{Bell2004,Faber2007,Brown2007,Ilbert2010,Brammer2011,Muzzin2013,Buitrago2013} there must also be processes which shut off star-formation within main sequence galaxies (i.e. quenching) which, to explain observations, must be a function of both mass and environment \citep{Peng2010,Darvish2016}.

@@

This paper focusses on the third question by deriving and interpreting the spatially resolved kinematics of the KDS galaxies, particularly the rotation velocities and velocity dispersions, using the [O~{\sc III}]$\lambda$5007 emission line, discussing what we can learn about the nature of galaxy formation at $z \sim 3.5$ and forming evolutionary links with lower redshift work.
We seek also to minimise the impact of systematic differences introduced by the differing approaches in defining and extracting kinematic parameters when interpreting these trends.  
By making use of KMOS we have been able to study [O~{\sc III}]$\lambda$5007 emission in 77 galaxies with integration times ranging between 7.5-9 hours on source, with these galaxies, which span the mass range $9.5 < log(M_{\star}/M_{\odot}) < 10.5$, roughly tripling the number of galaxies observed in IFS at $z > 3$. \\

@@

\begin{figure*}
    \centering \hspace{-1.3cm}
    \begin{subfigure}[h!]{0.5\textwidth}
        \centering
        \includegraphics[height=3.5in]{rest_colour.png}
    \end{subfigure} \hspace{+0.4cm}
    \begin{subfigure}[h!]{0.5\textwidth}
        \centering
        \includegraphics[height=3.5in]{main_sequence.png}
    \end{subfigure}
    \caption{{\it Left:} The distribution of 49 KDS galaxies (see \cref{subsubsec:sed_fitting}) in rest-frame UVJ colour space is plotted, with filled symbols showing galaxies detected in [O~{\sc III}]$\lambda$5007 and open symbols showing those which were not detected.
    Also plotted in this plane are $\sim4000$ galaxies in GOODS-S with $3.0 < z < 3.8$ (mirroring the KDS redshift range) from the 3D-{\em HST} survey, with the filled squares denoting the density in of galaxies in that region.
    We use the galaxy selection criteria defined in \protect\cite{Whitaker2012a} to highlight star-forming and quiescent regions (motivated by the age sequence of quiescent galaxies), finding that the KDS galaxies are all clearly in the star-forming region and overlap with the highest density of 3D-{\em HST} targets.
    {\it Right:} We plot the location of the same 49 KDS galaxies in the SFR versus M$_{\star}$ plane, using the same symbol convention. 
    The same GOODS-S galaxies from the 3D-{\em HST} survey \protect\citep{Brammer2012,Momcheva2016} at $3.0 < z < 3.8$ are plotted with the filled squares as a reference for the typical relationship between SFR and $M_{\star}$.
    The solid black lines and the dashed line show the $z\sim2.5$ broken power-law and quadratic fit to the main sequence respectively, described in \protect\cite{Whitaker2014}.
    We include the MS relation evaluated at $z=3.5$ (the median redshift of the KDS sample) described in \protect\cite{Speagle2014} and given in equation \protect\ref{eq:speagle_ms} throughout the text as the green line, with the discrepancy between the two relations representating the expected main sequence evolution between these redshifts. 
    Within the typical uncertainties (see error bars) the KDS sample is representative of $z\sim3.5$ SFGs.}
    \label{fig:main_sequence}
\end{figure*}

Our data for the 77 KDS targets were observed using KMOS, which is a second generation IFS mounted at Nasmyth focal plane on UT1 at the VLT.
The instrument has 24 moveable pickoff arms, each with an integrated IFU, which patrol a region 7.2$^{\prime}$ in diameter on the sky, providing considerable flexibility when selecting sources for a single pointing.
The light from each set of 8 IFUs is dispersed by a single spectrograph and recorded on a 2k$\times$2k Hawaii-2RG HgCdTe near-IR detector, so that the instrument is comprised of three effectively independent modules.
Each IFU has 14$\times$14 spatial pixels which are 0.2$^{\prime\prime}$ in size, and the central wavelength of the K-band grating has spectral resolution of $R \sim 4200$ (H-band $R \sim 4000$).
\subsubsection{Observations}\label{subsubsec:Obs}
To achieve the science goals of the KDS the target galaxies at $3 < z < 3.8$ were observed in both the K-band, into which the [O~{\sc III}]$\lambda$5007 and $H\beta$ lines are redshifted, and the H-band, into which the [O~{\sc II}]$\lambda$3727,$\lambda$3729 doublet is redshifted, to facilitate both dynamical and chemical abundance measurements.
The GOODS-S pointings were observed in the H and K-bands separately, however due to loss of observing time the SSA22 galaxies were observed with the KMOS HK filter, which has the disadvantage of effectively halving the spectral resolution, but allows for coverage of the H-band and K-band regions simultaneously. \\

@@

\subsubsection{SED fitting and main sequence}\label{subsubsec:sed_fitting}
We use SED modelling to constrain simultaneously the $M_{\star}$ and SFR of the KDS targets.
During the SED modelling we assume solar metallicity stellar templates and make use of \cite{Calzetti2000} reddening law with exponentially declining SFRs in both GOODS-S and SSA22.
A Chabrier IMF is used with a reduced set of BC03 \citep{Bruzual2003} templates in the fitting procedure.
We have also computed the quantities using 0.2Z$\odot$ templates, finding stellar masses for the galaxies which are on average 0.1 dex lower, but this change does not affect the conclusions of this work.
The median stellar mass for the full observed samples in both GOODS-S and SSA22 is $log(M_{\star}/M_{\odot}) = 10.0$.
In SSA22 29 targets (36\% of the full KDS sample) do not have SFR measurements due to having J and K-band detections lower than 2-$\sigma$ significance.
For these objects we are able to estimate robust stellar masses from the available photometry, noting that the median of stellar mass distribution is $\sim 0.3$ dex lower than the median stellar mass in GOODS-S. \\

In the left panel of Figure \ref{fig:main_sequence} we plot the 64\% of KDS galaxies with SFR measurements in the rest-frame {\it U-V} vs. {\it V-J} colour space.
This is a commonly used diagnostic plane for selecting star-forming and quiescent galaxies \citep[e.g.][]{Williams2009,Brammer2011,Whitaker2012a} with the age gradients of the stars within quiescent galaxies placing them in a different region of the plane to those which are actively forming stars.
The selection criteria defined in \cite{Whitaker2012a} (which evolve only gently with redshift) separate quiescent and star-forming regions, which are indicated by the black wedge.
We also make use of the rest-frame colours of $\sim7000$ primarily star-forming galaxies located in GOODS-S between $2.5 < z < 3.5$ from the 3D-{\em HST} survey \citep{Momcheva2016}.
The filled squares indicate the density of 3D-{\em HST} targets in colour spaceand we observe that the peak density location is consistent with the location of the KDS targets, all of which are in the star-forming region.

In the right panel of Figure \ref{fig:main_sequence} we plot the M$_{\star}$ and SFR `main sequence' for the KDS galaxies with SFR measurements, in combination with the derived physical properties of $\sim 10,000$ SFGs at $2.5 < z < 3.5$  (based upon the `z\_best classification flag') from the 3D-{\em HST} survey \citep{Brammer2012,Momcheva2016}.
We also plot both the linear-break and quadratic $z\sim 2.5$ main sequence fits to the 3D-{\em HST} data described in \cite{Whitaker2014} with the solid and dashed black lines as well as the main sequence relation described in \cite{Speagle2014} given in equation \ref{eq:speagle_ms}, evaluated at $z\sim3.5$ where the age of the universe is 1.77 Gyr, with the green line.

@@

The difference in position of these relations highlights the main sequence evolution towards higher SFRs at fixed $M_{\star}$ between $z\sim2.5-3.5$.
The KDS galaxies scatter, within the errors, consistently above and below the z$\sim3$ main sequence.

When taken together, both panels indicate that the KDS sample is representatitve of typical SFGs at $z>3$.

@@

ID              & RA       & Dec       & z     & K$_{AB}$     & $log(M_{\star}/M_{\odot})^{a}$ & SFR$_{SED}$[$M_{\odot}yr^{-1}]$$^{b}$ & $b/a$ & i$^{\circ}$$^{c}$ & PA$_{morph}^{\circ}$ & R$_{1/2}$(kpc)$^{d}$ \\

@@

We plot the relationship between $V_{C}$ and $M_{\star}$ for the isolated field sample in the left panel of Figure \ref{fig:tf_relation}.
In \cite{Harrison2017}, the inverse stellar mass Tully-Fisher relation relation is fit to $\sim400$ $9.5 < log(M_{\star}/M_{\odot}) < 10.5$ star-forming galaxies at $z\sim0.9$, measured to be rotationally dominated with $V_{C}/\sigma_{int} > 1$.
The data are used to constrain parameters `a' and `b' in the equation $logV_{C}=b+a[logM_{\star} - 10.0]$ (see their section 4.2) finding $a = 0.33 \pm 0.11$ and $b = 2.12 \pm 0.04$.
We plot this best fit relation with the solid green line, with the green shaded region giving the typical scatter of 0.2 dex along the velocity axis.
These $z\sim0.9$ parameters are consistent with the coefficients measured in the local universe, $a_{z=0} = 0.278 \pm 0.010$ and $b_{z=0} = 2.142 \pm 0.004$ , for a sample of $z<0.1$ disks from \cite{Reyes2011}, which are in a similar mass range to KROSS and traced with H$\alpha$ emission.
In \citep{Reyes2011} $V_{C}$ has been extracted at the same radius and we plot this $z\sim 0.1$ local relation as the dashed black line in the left panel of Figure \ref{fig:tf_relation}.
The agreement between these parameters derived at $z\sim0$ and $z\sim0.9$ suggests that there is no evolution of the slope/normalisation of the stellar mass Tully-Fisher relation for rotationally dominated star-forming galaxies between these limits. \\

@@

In a rotationally supported system, the circular velocity is set by the requirement to support the total mass in the system, i.e. the combination of gas mass, stellar mass and dark matter mass, against gravitational collapse.
$V_{C}$ increases with increasing total mass and so we would expect the systems with larger average stellar mass, assuming that these are indicative of systems with greater total mass, to have larger $V_{C}$, which appears generally to be the case in the right panel of Figure \ref{fig:tf_relation} where the KMOS$^{3D}$, GHASP and SINS galaxies have the largest inferred $V_{C}$ values.
Using the average $M_{\star}$ values and velocity extraction radii in the isolated field sample, $log(M_{\star}/M_{\odot})=10.0$ and $2R_{1/2} = 3.2kpc$ respectively, and assuming simple, circular Keplerian orbits where the rotational motions alone support the mass of the system, we can calculate a rough lower limit of $\left<V_{C}\right>$ $>$ $125kms^{-1}$ for the baryonic material in the galaxies (since the inclusion of gas mass and dark matter mass would raise this estimate).
Indeed this value is similar to the mean $V_{C}$ value found in the KROSS sample for $log(M_{\star}/M_{\odot})=10.0$ galaxies at $z\sim1$. \\

@@

We proceed to consider the cause of the high number of dispersion dominated galaxies in our sample and the obvious candidate is the increase of velocity dispersion with redshift \citep[e.g.][]{Genzel2006,Genzel2008,ForsterSchreiber2009,Law2009,Gnerucci2011,Epinat2012,Wisnioski2015}.
There are also some galaxies in our sample where the observed velocity field has obvious rotational structure and clearly reaches flattening (e.g. see \cref{fig:dispersion_dominated_galaxies} lbg\_24 with $log(M_{\star}/M_{\odot})=9.75$), with inferred $V_{C}$ smaller than $\sigma_{int}$.
This suggests again that the increase in random motions could influence the rotational velocities and that the accumulation of a massive stellar population is necessary to stabilise a galaxy \citep[e.g.][]{Law2009,Law2012b,Law2012c,Newman2013,Wisnioski2015}.
These ideas are explored in the following sections.

@@

The mean KDS datapoint is in agreement with the scaling relation, plotted with the grey lines for $V_{C} = 125kms^{-1}$ and $log(M_{\star}/M_{\odot})=10.0,10.3,10.6$ (note we have not shifted the datapoints to conform with a single $M_{\star}$ value as per \cite{Wisnioski2015}).
The lower $M_{\star}$ tracks suggest a flatter evolution of $\sigma_{int}$ with redshift, and indeed the surveys with lower average $M_{\star}$ (MASSIV, DYNAMO, LAW 2009, KROSS, AMAZE) have higher $\sigma_{int}$ than the surveys with larger average $M_{\star}$ (GHASP, KMOS$^{3D}$, SINS), although the exact values are sensitive to the choice of $Q_{crit}$ (shown to be $\sim1$ for the gas-rich disks observed at high-z e.g. \citealt{ForsterSchreiber2006,Genzel2011,Newman2013}) and $V_{C}$ in the equation shown in the top right of the left panel of Figure \ref{fig:sigma_and_v_sigma_w_redshift} (see \cref{sec:discussion}).
The tracks plotted in Figure \ref{fig:sigma_and_v_sigma_w_redshift} suggest the shape of the $\sigma_{int}$ evolution in galaxies of a particular stellar mass in the context of the equilibrium model, with these new results from the KDS providing strong observational constraints on the internal dynamics of main sequence galaxies between $z=3-3.7$.
